
\documentclass{article}
\begin{document} 

For testing, we used such signal sources as Sr-90, Na-22, LED, laser.
The following were measured: signal amplitude attenuation, time difference resolution, signal delay time along the boards, and the signal rising time was monitored.
From the measurement results, the following conclusions were drawn from a technical point of view:

1. Flexible PCBs, along with ease of use on the one hand, showed waveform distortion when bent, on the other hand.

2. In order to prevent the rapid destruction of the PCB with repeated bends due to the fragility of the wiring, the tests used the connection of the PCB with photodetectors using short wires.

3. Connectors along the boards for reading signals are reliable and convenient, gold connectors for read-out are also quite reliable, but not very firmly attached to the board.

4. External light affects measurements. In order to minimize this influence, the test setup was equipped with an insulating box.

5. There was no apparent jump in amplitude when switching from one board to another, associated with electrical connections, although signal distortions due to mechanical deformations of the flat cable (to ensure the connection of two boards) and the PCB occurred frequently, which led to a noticeable drop in amplitude.

6. Signal measurements on the second board showed an inconsistent signal amplitude change, likely related to the electrical wiring diagram.

According to the measurement results:

1.Amplitude attenuation measurements showed \textbf{'...percent'} attenuation.

2. Time difference resolution measurement showed excellent results (50-100 ps) on the first board and unsatisfactory results       (300-400 ps) on the second board. Apparently, this is due to an increase in reading errors at larger distances. In addition, on the second board, waveform distortions were observed more often than on the first. 

3. Comparison of the measured signal delay along the length of the boards and the delay generated by the corresponding cable length shows an excess of approx. 3 ns (12.5 ns vs 9.5 ns).

\end{document}